IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex
nit
nits
target-Inside -> target-inside

For our first example, here is a program which spawns a new isolated task,
and then sends it a mutable reference:
\begin{align*}
    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
    & |in TI (send (IT i) l (IT (ref true)))|
\end{align*}
For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
message, and then \textbf{send}s the task a mutable reference |(ref
true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
could be used to violate information flow control if the tasks had
differing labels.  At this point, the designer of an IFC system might
add label checks to mutable references, to check the labels of the
reader and writer. While this solves the leak, for languages like
JavaScript, where references are prevalently used, this also dooms the
performance of the system.

@@

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fix te
tE   ::= tHole | tE te | tv tE | if tE then te else te | ref tE | !tE | tE := te | tv := tE | fix tE
te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
let tx = te1 in te2  @= (\tx.te2) te1
\end{code}
\begin{mathpar}

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of
      both languages to allow for embeddings terms in one language to
      be embedded in the other, as
      in~\cite{Matthews:2007:OSM:1190216.1190220}.
    %
In the target language, an IFC expression appears as |TI ie| (``\Red{T}arget-outside,
IFC-inside''); in the IFC language, a target language expression appears as |IT
te| ( ``{\color{blue}{I}}FC-outside, target-Inside'').
    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task list, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.  The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
    Figure~\ref{fig:scheduler} defines two concrete schedulers.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}

>>>>

As an example, here is a program which spawns a new isolated task,
and then sends it a mutable reference:
\begin{align*}
    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
    & |in TI (send (IT i) l (IT (ref true)))|
\end{align*}
For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
message, and then \textbf{send}s the task a mutable reference |(ref
true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
could be used to violate information flow control if the tasks had
differing labels.  At this point, the designer of an IFC system might
add label checks to mutable references, to check the labels of the
reader and writer. While this solves the leak, for languages like
JavaScript, where references are prevalently used, this also dooms the
performance of the system.

@@

\begin{figure}[t]
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | fix te
tE   ::= tHole | tE te | tv tE | if tE then te else te | ref tE | !tE | tE := te | tv := tE | fix tE
te1 ; te2            @= (\tx.te2) te1  where  tx notmember FV(te2)
let tx = te1 in te2  @= (\tx.te2) te1
\end{code}
\begin{mathpar}

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of
      both languages to allow for embeddings terms in one language to
      be embedded in the other, as
      in~\cite{Matthews:2007:OSM:1190216.1190220}.
    %
In the target language, an IFC expression appears as |TI ie| (``\Red{T}arget-outside,
IFC-inside''); in the IFC language, a target language expression appears as |IT
te| ( ``{\color{blue}{I}}FC-outside, target-inside'').
    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task list, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.  The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
    Figure~\ref{fig:scheduler} defines two concrete schedulers.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}
